State of the Practice for Medical Imaging Software Based on Open Source Repositories

### 2025-01-28 StateOfPractice/Papers/SOP_MI_CritReviewsBioMedEng/SOP_MI_OSR.tex
Cleanup comments in tex file, add jpg versions of figures

%\documentclass[doubleblind,12pt, 3p, times]{elsarticle}
\documentclass[12pt, 3p, times]{elsarticle}

@@

% prepared for: Journal of Imaging Informatics in Medicine
% https://link.springer.com/journal/10278

@@

@@

%% Title, authors and addresses

%% use the tnoteref command within \title for footnotes;
%% use the tnotetext command for theassociated footnote;
%% use the fnref command within \author or \affiliation for footnotes;
%% use the fntext command for theassociated footnote;
%% use the corref command within \author for corresponding author footnotes;
%% use the cortext command for theassociated footnote;
%% use the ead command for the email address,
%% and the form \ead[url] for the home page:
%% \title{Title\tnoteref{label1}}
%% \tnotetext[label1]{}
%% \author{Name\corref{cor1}\fnref{label2}}
%% \ead{email address}
%% \ead[url]{home page}
%% \fntext[label2]{}
%% \cortext[cor1]{}
%% \affiliation{organization={},
%%            addressline={}, 
%%            city={},
%%            postcode={}, 
%%            state={},
%%            country={}}
%% \fntext[label3]{}

@@

%% use optional labels to link authors explicitly to addresses:
%% \author[label1,label2]{}
%% \affiliation[label1]{organization={},
%%             addressline={},
%%             city={},
%%             postcode={},
%%             state={},
%%             country={}}
%%
%% \affiliation[label2]{organization={},
%%             addressline={},
%%             city={},
%%             postcode={},
%%             state={},
%%             country={}}

%\author{Anonymous}
\author[CAS]{Spencer Smith}
\author[CAS]{Ao Dong}
\author[CAS]{Jacques Carette}
\author[ECE]{Michael Noseworthy}

\affiliation[CAS]{organization={McMaster University, Computing and Software
Department}, %Department and Organization
            addressline={1280 Main Street West}, 
            city={Hamilton},
            postcode={L8S 4K1}, 
            state={Ontario},
            country={Canada}}

\affiliation[ECE]{organization={McMaster University, Electrical and Computer Engineering}, %Department and Organization
            addressline={1280 Main Street West}, 
            city={Hamilton},
            postcode={L8S 4K1}, 
            state={Ontario},
            country={Canada}}

@@

%%Graphical abstract
%\begin{graphicalabstract}
%\includegraphics{grabs}
%\end{graphicalabstract}

%%Research highlights
%\begin{highlights}
%\item Research highlight 1
%\item Research highlight 2
%\end{highlights}

@@

%% \linenumbers

@@

%\subsection{Research Questions} \label{sec_motivation}

@@

%\subsection{Scope} \label{sec_scope}

@@

We have a standard set of questions designed to assess the qualities of any
research software project~\cite{SmithEtAl2021, SmithAndMichalski2022}. We build
off prior work to assess the state of the practice for such domains as Lattice
Boltzmann Solvers \cite{SmithEtAl2024}, Geographic Information Systems
\cite{smith2018state}, Mesh Generators \cite{smith2016state}, Seismology
software \cite{Smith2018Seismology}, and Statistical software for psychology
\cite{smith2018statistical}.  %% DOUBLE BLIND 
We maintain the previous
constraint that the work load for measuring a given domain should take around
one person-month's worth of effort ($20$ working days at $8$ person-hours per
day).

We identify a list of potential packages (through online searches) which is then
filtered and vetted by a domain expert. We aim for roughly $30$ packages. For
each remaining package, we measure its qualities via a grading
template~\cite{SmithEtAl2021}.    %%DOUBLE BLIND
This data is used to rank the projects with the
Analytic Hierarchy Process (AHP).  We summarize further details on the
interaction with the domain expert, software qualities, grading the software and
AHP below and in longer form in Smith et al.\ (2024)~\cite{SmithEtAl2024_MI_SOP}.
%% DOUBLE BLIND

@@

The Domain Expert vets the proposed list because online resources can be
inaccurate.  The expert also vets the AHP ranking.  Our Domain Expert (and
paper co-author) is Dr.\ Michael Noseworthy, Professor of Electrical and
Computer Engineering at McMaster University, Co-Director of the McMaster School
of Biomedical Engineering, and Director of Medical Imaging Physics and
Engineering at St.\ Joseph's Healthcare, Hamilton, Ontario, Canada.  %%DOUBLE BLIND

@@

We use an existing template \cite{SmithEtAl2021} %% DOUBLE BLIND
that is designed to measure the
aforementioned qualities. To stay within our given measurement time frame, each
package gets up to five hours of time.  Project developers can be contacted for
help regarding installation, if necessary, but we impose a cap of about two
hours on the installation process.  We explicitly note any software that cannot be installed, but for completeness we still measure it for the remaining qualities, since only reliability and robustness require running the software. Figure~\ref{fg_grading_template_example}
shows an excerpt of the measurement spreadsheet.  The rows are the measures and
the columns correspond to the software packages.  Dong (2021)~\cite{Dong2021-Data}
provides the full set of measurement data.   %%DOUBLE BLIND

\begin{figure*}[ht!]
\includegraphics[scale=0.67]{template.pdf}
\caption{Grading template example}
\label{fg_grading_template_example}
\end{figure*}

@@

The grader, after answering questions for each quality assigns an overall
score (between 1 and 10) based on the answers.  Several of the qualities use
the word ``surface'' to highlight that these particular qualities are a shallow
measure.  For example, usability is not measured using user studies.
Instead, we look for signs that the developers considered usability.
We use two freeware tools to collect repository related data:
\href{https://github.com/tomgi/git_stats}{GitStats} and
\href{https://github.com/boyter/scc}{Sloc Cloc and Code (scc)}.  Further
details on quality measurement are provided in Smith et al.\ (2024) \cite{SmithEtAl2024_MI_SOP}. 
%% DOUBLE BLIND

@@

The repository-based measurements are incomplete because they don't generally
capture the development process, the developer pain points, the perceived
threats to software quality, and the developers' strategies to address these
threats.  Therefore, part of our methodology involves interviewing developers.
We based our interviews on a list of 20 questions, which can be found in
Smith et al. \cite{SmithEtAl2021}. %%DOUBLE BLIND
Some questions are about the background of the software, the development teams,
the interviewees, and how they organize their projects.  We also ask about the
developer's understanding of the users. Additional questions focus on the current and
past difficulties, and the solutions the team has found, or plan to try. We also
discuss documentation, both with respect to how it is currently done, and how it
is perceived. A few questions are about specific software qualities, such as
maintainability, understandability, usability, and reproducibility. The
interviews are semi-structured based on the question list.

@@

In Table~\ref{tab_final_list} the projects are sorted in descending order of
lines of code.  We found the initial release dates (Rlsd) for most projects and
marked the two unknown dates with ``?''. The date of the last update is the date
of the latest update, at the time of measurement. We found funding information
(Fnd) for only eight projects.  For the Number Of Contributors (NOC) we
considered anyone who made at least one accepted commit as a contributor. The
NOC is not usually the same as the number of long-term project members, since
many projects received change requests and code from the community.  With
respect to the OS, 25 packages work on all three OSs: Windows (W), macOS (M),
and Linux (L). Although the usual approach to cross-platform compatibility was
to work natively on multiple OSes, five projects achieved platform-independence
via web applications. The full measurement data for all packages is available on
\href{https://data.mendeley.com/datasets/k3pcdvdzj2/1} {Mendeley Data}.  
%% DOUBLE BLIND

@@

\begin{figure*}[ht!]
\includegraphics[scale=0.47]{overall_scores.pdf}
\caption{Overall AHP scores with an equal weighting for all 9 software qualities}

@@

The overall score is based on the measurement of the identified qualities. Full
details of how the projects compare for each quality can be found in Smith et
al.~\cite{SmithEtAl2024_MI_SOP}. %% DOUBLE BLIND

@@

We interview developers, as described in Section~\ref{sec_interview_methods}, to answer \rqref{RQ_CompareToolsProjMngmnt} (tool usage),
\rqref{RQ_CompareMethodologies} (methodology) and \rqref{RQ_PainPoints} (pain
points). Requests were sent to all 29 projects.  Nine developers from eight of
the projects agreed to participate: \textit{3D Slicer}, \textit{INVESALIUS 3},
\textit{dwv}, \textit{BioImage Suite Web}, \textit{ITK-SNAP},
\textit{MRIcroGL}, \textit{Weasis}, and \textit{OHIF}. We spent about 90
minutes for each interview. The full interview answers can be
found in Dong (2021)~\cite{Dong2021}. %%DOUBLE BLIND

@@

\paragraph{CI/CD} 
Only 17\% of MI projects use CI/CD tools. We estimated this using artifacts
present in the repository -- actual usage may be higher as some tools are
entirely external. This was the case for a study of Lattice Boltzmann Method
(LBM) software~\cite{Michalski2021}. %%DOUBLE BLIND
This contrasts with the high frequency of guidelines recommending continuous
integration
\cite{BrettEtAl2021, ThielEtAl2020, vanGompelEtAl2016, Brown2015, Zadka2018}.
A recent survey~\cite{CarverEtAl2022} of practitioners (rather than projects)
suggests higher use of CI/CD with 54\% of respondents indicating that they use
it.

\paragraph{Documentation} The most popular (mentioned by about 30\% of
developers) were forum discussions and videos.  The second most popular options
(20\%) were GitHub, wiki pages, workshops, and social media. The least
frequently mentioned options (about 10\% of developers) included writing books,
and Google forms.  As a point of contrast, LBM software most often uses API
document generation tools, like doxygen and sphinx~\cite{Michalski2021}. %%DOUBLE BLIND

@@

No interviewee mentioned a strictly defined project management process. The most
common approach was issue-driven via bug reports and feature requests.
Dong (2021)~\cite{Dong2021} %%DOUBLE BLIND
provides details on the specific approaches used by the interviewees.
% JC: I don't think this level of per-project detail makes sense in this
% review article - it should be about stats and trends, not reporting on
% minute details. We could refer the reader to Ao's thesis for the details.
% 
% SS: I've revised the text to not include the details
% The
% most common approach was following the issues, such as bugs and feature
% requests. The \textit{3D Slicer} team had weekly meetings to discuss
% the goals for the project. The \textit{INVESALIUS 3} team relied on the
% GitHub process for their project management while the \textit{ITK-SNAP} 
% team had a fixed six-month release pace. Only the interviewee from 
% \textit{OHIF} 
% mentioned the team having a project manager. The \textit{3D Slicer} team and
% \textit{BioImage Suite Web} team do nightly builds and tests. The \textit{OHIF}
% developer believes that a better project management process can improve junior
% developer efficiency while also improving internal and external communication.

Less than half of the projects used unit testing, even
though the interviewees believed that testing (including usability tests) was
the top approach to improve correctness, usability, and reproducibility.  This
level of testing matches what was observed for LBM
software~\cite{Michalski2021} %%DOUBLE BLIND
and is apparently greater than the level of
testing for ocean modelling software~\cite{JungEtAl2022}.

@@

\item[P\refstepcounter{pnum}\thepnum \label{P_LackDevTime}:] \textbf{Lack of
Development Time:} This was felt to be the most significant obstacle, and
is not uncommon
\cite{SmithEtAl2024, WieseEtAl2019, PintoEtAl2018, PintoEtAl2016}.
%DOUBLE BLIND

\item[P\refstepcounter{pnum}\thepnum \label{P_LackFunding}:] \textbf{Lack of
Funding:} As research software is not yet seen as essential infrastructure,
there is an ongoing struggle to attract funding to build and, even harder, maintain
research software. This is a common complaint~\cite{SmithEtAl2024, GewaltigAndCannon2012, Goble2014, KaterbowAndFeulner2018}. %,  %DOUBLE BLIND
Software output is not always counted when judging the academic excellence of
academics, which forces researchers who write software to spend extra time on
publicity~\cite{WieseEtAl2019}. In some domains, like
biology~\cite{HowisonAndBullard2016}, software is infrequently cited even when
used pervasively. In other words, there is a lack of a formal reward system for
research software~\cite{PintoEtAl2018}.

@@

At least to some extent the problems for MI software users are due to holes in
their knowledge of software and computing technology, and sometimes also
lack of expertize in their domain to be able to adequately use the software
\cite{WieseEtAl2019}. 
A similar pattern has been observed during interviews with
LBM software developers \cite{SmithEtAl2024}. %%DOUBLE BLIND

@@

%JC: I'm aware of too many caveats wrt this recommendation, so I am taking
% it out.
%SS: I agree with the removal.
%
%\item \textbf{Remove privacy from sensitive data.} For data with sensitive
%information, a team can ask the data owner to remove such information or add
%noise to protect privacy. One example is using de-identified copies of medical
%images for testing.

@@

The pervasive use of such tools to enforce documentation standards partially
explains the relatively high quality of software in the Comprehensive R Archive
Network (CRAN)~\cite{SmithEtAl2018_StatSoft}. %%DOUBLE BLIND

@@

The measurement process used has previously been shown to be reasonably
reproducible.
%% DOUBLE BLIND
Smith et al.~\cite{SmithEtAl2016} reports grading five software products by two reviewers.
Their rankings were almost identical. The relative comparisons in the AHP
results will be consistent between graders, as long as the evaluators are
consistent in their judgement.

@@

If the results of a study can be generalized to other situations, then the study
is externally valid \cite{RunesonAndHost2009}.  In other words, we cannot
generalize our results if there is a fundamental difference between the
development of MI software and other research software.  Although there are
differences, like the importance of data privacy for MI data, we found the
approach to developing LBM software \cite{SmithEtAl2024} 
%% DOUBLE BLIND
and MI software to be similar.  Except for
the domain specific aspects, the trends observed in the current study are
similar to that for other research software.

@@

\begin{table*}[ht!]
    %\begin{center}
    \caption{Top performers for each quality (sorted by order of quality
    measurement)}
    \renewcommand{\arraystretch}{1.8}
    \begin{tabular}{ p{3cm}p{12.5cm} }
        \toprule

@@

        \bottomrule
    \end{tabular}
    \label{topperformerstable}
    %\end{center}
\end{table*}

@@

%% DOUBLE BLIND
We would like to thank Peter Michalski and Oluwaseun Owojaiye for fruitful
discussions on topics relevant to this paper.

>>>>

%\documentclass[doubleblind,12pt, 3p, times]{elsarticle}
%\documentclass[draft, review, 12pt, 3p, times]{elsarticle} %so figures are blank, double spaced
\documentclass[12pt, 3p, times]{elsarticle}

@@

@@

%\DeclareGraphicsExtensions{.pdf} %use pdf version of figures
\DeclareGraphicsExtensions{.jpg} %use jpg versions (high resolution won't actually fit)

@@

@@

\author[CAS]{Spencer Smith}
\author[CAS]{Ao Dong}
\author[CAS]{Jacques Carette}
\author[ECE]{Michael Noseworthy}

\affiliation[CAS]{organization={McMaster University, Computing and Software
Department}, 
            addressline={1280 Main Street West}, 
            city={Hamilton},
            postcode={L8S 4K1}, 
            state={Ontario},
            country={Canada}}

\affiliation[ECE]{organization={McMaster University, Electrical and Computer Engineering}, 
            addressline={1280 Main Street West}, 
            city={Hamilton},
            postcode={L8S 4K1}, 
            state={Ontario},
            country={Canada}}

@@

@@

@@

@@

@@

We have a standard set of questions designed to assess the qualities of any
research software project~\cite{SmithEtAl2021, SmithAndMichalski2022}. We build
off prior work to assess the state of the practice for such domains as Lattice
Boltzmann Solvers \cite{SmithEtAl2024}, Geographic Information Systems
\cite{smith2018state}, Mesh Generators \cite{smith2016state}, Seismology
software \cite{Smith2018Seismology}, and Statistical software for psychology
\cite{smith2018statistical}.  We maintain the previous constraint that the work
load for measuring a given domain should take around one person-month's worth of
effort ($20$ working days at $8$ person-hours per day).

We identify a list of potential packages (through online searches) which is then
filtered and vetted by a domain expert. We aim for roughly $30$ packages. For
each remaining package, we measure its qualities via a grading
template~\cite{SmithEtAl2021}.  This data is used to rank the projects with the
Analytic Hierarchy Process (AHP).  We summarize further details on the
interaction with the domain expert, software qualities, grading the software and
AHP below and in longer form in Smith et al.\
(2024)~\cite{SmithEtAl2024_MI_SOP}.

@@

The Domain Expert vets the proposed list because online resources can be
inaccurate.  The expert also vets the AHP ranking.  Our Domain Expert (and paper
co-author) is Dr.\ Michael Noseworthy, Professor of Electrical and Computer
Engineering at McMaster University, Co-Director of the McMaster School of
Biomedical Engineering, and Director of Medical Imaging Physics and Engineering
at St.\ Joseph's Healthcare, Hamilton, Ontario, Canada.

@@

We use an existing template \cite{SmithEtAl2021} that is designed to measure the
aforementioned qualities. To stay within our given measurement time frame, each
package gets up to five hours of time.  Project developers can be contacted for
help regarding installation, if necessary, but we impose a cap of about two
hours on the installation process.  We explicitly note any software that cannot
be installed, but for completeness we still measure it for the remaining
qualities, since only reliability and robustness require running the software.
Figure~\ref{fg_grading_template_example} shows an excerpt of the measurement
spreadsheet.  The rows are the measures and the columns correspond to the
software packages.  Dong (2021)~\cite{Dong2021-Data} provides the full set of
measurement data.

\begin{figure*}[ht!]
\includegraphics[scale=0.67]{template}
\caption{Grading template example}
\label{fg_grading_template_example}
\end{figure*}

@@

The grader, after answering questions for each quality assigns an overall
score (between 1 and 10) based on the answers.  Several of the qualities use
the word ``surface'' to highlight that these particular qualities are a shallow
measure.  For example, usability is not measured using user studies.
Instead, we look for signs that the developers considered usability.
We use two freeware tools to collect repository related data:
\href{https://github.com/tomgi/git_stats}{GitStats} and
\href{https://github.com/boyter/scc}{Sloc Cloc and Code (scc)}.  Further
details on quality measurement are provided in Smith et al.\ (2024) \cite{SmithEtAl2024_MI_SOP}.

@@

The repository-based measurements are incomplete because they don't generally
capture the development process, the developer pain points, the perceived
threats to software quality, and the developers' strategies to address these
threats.  Therefore, part of our methodology involves interviewing developers.
We based our interviews on a list of 20 questions, which can be found in Smith
et al. \cite{SmithEtAl2021}.  Some questions are about the background of the
software, the development teams, the interviewees, and how they organize their
projects.  We also ask about the developer's understanding of the users.
Additional questions focus on the current and past difficulties, and the
solutions the team has found, or plan to try. We also discuss documentation,
both with respect to how it is currently done, and how it is perceived. A few
questions are about specific software qualities, such as maintainability,
understandability, usability, and reproducibility. The interviews are
semi-structured based on the question list.

@@

In Table~\ref{tab_final_list} the projects are sorted in descending order of
lines of code.  We found the initial release dates (Rlsd) for most projects and
marked the two unknown dates with ``?''. The date of the last update is the date
of the latest update, at the time of measurement. We found funding information
(Fnd) for only eight projects.  For the Number Of Contributors (NOC) we
considered anyone who made at least one accepted commit as a contributor. The
NOC is not usually the same as the number of long-term project members, since
many projects received change requests and code from the community.  With
respect to the OS, 25 packages work on all three OSs: Windows (W), macOS (M),
and Linux (L). Although the usual approach to cross-platform compatibility was
to work natively on multiple OSes, five projects achieved platform-independence
via web applications. The full measurement data for all packages is available on
\href{https://data.mendeley.com/datasets/k3pcdvdzj2/1} {Mendeley Data}.

@@

\begin{figure*}[ht!]
\includegraphics[scale=0.47]{overall_scores}
\caption{Overall AHP scores with an equal weighting for all 9 software
qualities}

@@

The overall score is based on the measurement of the identified qualities. Full
details of how the projects compare for each quality can be found in Smith et
al.~\cite{SmithEtAl2024_MI_SOP}.

@@

We interview developers, as described in Section~\ref{sec_interview_methods}, to
answer \rqref{RQ_CompareToolsProjMngmnt} (tool usage),
\rqref{RQ_CompareMethodologies} (methodology) and \rqref{RQ_PainPoints} (pain
points). Requests were sent to all 29 projects.  Nine developers from eight of
the projects agreed to participate: \textit{3D Slicer}, \textit{INVESALIUS 3},
\textit{dwv}, \textit{BioImage Suite Web}, \textit{ITK-SNAP}, \textit{MRIcroGL},
\textit{Weasis}, and \textit{OHIF}. We spent about 90 minutes for each
interview. The full interview answers can be found in Dong
(2021)~\cite{Dong2021}.

@@

\paragraph{CI/CD} Only 17\% of MI projects use CI/CD tools. We estimated this
using artifacts present in the repository -- actual usage may be higher as some
tools are entirely external. This was the case for a study of Lattice Boltzmann
Method (LBM) software~\cite{Michalski2021}.  This contrasts with the high
frequency of guidelines recommending continuous integration \cite{BrettEtAl2021,
ThielEtAl2020, vanGompelEtAl2016, Brown2015, Zadka2018}.  A recent
survey~\cite{CarverEtAl2022} of practitioners (rather than projects) suggests
higher use of CI/CD with 54\% of respondents indicating that they use it.

\paragraph{Documentation} The most popular (mentioned by about 30\% of
developers) were forum discussions and videos.  The second most popular options
(20\%) were GitHub, wiki pages, workshops, and social media. The least
frequently mentioned options (about 10\% of developers) included writing books,
and Google forms.  As a point of contrast, LBM software most often uses API
document generation tools, like doxygen and sphinx~\cite{Michalski2021}.

@@

No interviewee mentioned a strictly defined project management process. The most
common approach was issue-driven via bug reports and feature requests.  Dong
(2021)~\cite{Dong2021} provides details on the specific approaches used by the
interviewees.

Less than half of the projects used unit testing, even though the interviewees
believed that testing (including usability tests) was the top approach to
improve correctness, usability, and reproducibility.  This level of testing
matches what was observed for LBM software~\cite{Michalski2021} and is
apparently greater than the level of testing for ocean modelling
software~\cite{JungEtAl2022}.

@@

\item[P\refstepcounter{pnum}\thepnum \label{P_LackDevTime}:] \textbf{Lack of
Development Time:} This was felt to be the most significant obstacle, and is not
uncommon \cite{SmithEtAl2024, WieseEtAl2019, PintoEtAl2018, PintoEtAl2016}.

\item[P\refstepcounter{pnum}\thepnum \label{P_LackFunding}:] \textbf{Lack of
Funding:} As research software is not yet seen as essential infrastructure,
there is an ongoing struggle to attract funding to build and, even harder,
maintain research software. This is a common complaint~\cite{SmithEtAl2024,
GewaltigAndCannon2012, Goble2014, KaterbowAndFeulner2018}.  Software output is
not always counted when judging the academic excellence of academics, which
forces researchers who write software to spend extra time on
publicity~\cite{WieseEtAl2019}. In some domains, like
biology~\cite{HowisonAndBullard2016}, software is infrequently cited even when
used pervasively. In other words, there is a lack of a formal reward system for
research software~\cite{PintoEtAl2018}.

@@

At least to some extent the problems for MI software users are due to holes in
their knowledge of software and computing technology, and sometimes also lack of
expertize in their domain to be able to adequately use the software
\cite{WieseEtAl2019}.  A similar pattern has been observed during interviews
with LBM software developers \cite{SmithEtAl2024}.

@@

@@

The pervasive use of such tools to enforce documentation standards partially
explains the relatively high quality of software in the Comprehensive R Archive
Network (CRAN)~\cite{SmithEtAl2018_StatSoft}.

@@

The measurement process used has previously been shown to be reasonably
reproducible.  Smith et al.~\cite{SmithEtAl2016} reports grading five software
products by two reviewers.  Their rankings were almost identical. The relative
comparisons in the AHP results will be consistent between graders, as long as
the evaluators are consistent in their judgement.

@@

If the results of a study can be generalized to other situations, then the study
is externally valid \cite{RunesonAndHost2009}.  In other words, we cannot
generalize our results if there is a fundamental difference between the
development of MI software and other research software.  Although there are
differences, like the importance of data privacy for MI data, we found the
approach to developing LBM software \cite{SmithEtAl2024} and MI software to be
similar.  Except for the domain specific aspects, the trends observed in the
current study are similar to that for other research software.

@@

\begin{table*}[ht!]
    \caption{Top performers for each quality (sorted by order of quality
    measurement)}
    \renewcommand{\arraystretch}{1.8}
    \begin{tabular}{ p{3cm}p{12.5cm} }
        \toprule

@@

        \bottomrule
    \end{tabular}
    \label{topperformerstable}
\end{table*}

@@

We would like to thank Peter Michalski and Oluwaseun Owojaiye for fruitful
discussions on topics relevant to this paper.
